Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-02 paper/paper.tex
Change equation to float

When the memory available on a system is less than $\mathbf{S} \times \mathbf{N}$, Revolve provides
an optimal strategy to solve for the adjoint field by storing a subset of the $\mathbf{N}$ total checkpoints
and recomputing the remaining ones. The overhead introduced by this method can be broken down into
the recomputation overhead $\mathbf{O}_R$ and the storage overhead $\mathbf{O}_S$. The recomputation
overhead is largely fixed and given by the following relationship (TODO cite revolve):
\begin{strip}
\begin{equation}
\mathbf{O}_R(N, M) = \begin{cases}
      N(N-1) /2, & \text{if}\ M=1 \\
      \min\limits_{1<=\widetilde{N}<=N} \{\widetilde{N} + \mathbf{O}_R(\widetilde{N}, M) + \mathbf{O}_R(N-\widetilde{N}, M-1)\}, & \text{if}\ M>1
    \end{cases}
    \label{eqn:recompute}
\end{equation}
\end{strip}
where M is the number of checkpoints that can be stored in memory. Note that for $M >=N$, $\mathbf{O}_R$
would be zero. For $M < N$, $\mathbf{O}_R$ goes up rather quickly as M is reduced in relation to N.

In a perfect implementation, the storage overhead $\mathbf{O}_S$ might be zero, since the computation could
be done "in-place", but in practice, checkpoints are generally stored in a separate section of memory and they
need to be transferred to a "computational" section of the memory where the compute is performed, and then
the results copied back to the checkpointing memory. This copying is a common feature of checkpointing
implementations, and might pose a non-trivial overhead in scenarios where the computation is heavily bandwidth-bound. 
This storage overhead is given by:
\begin{equation}
\mathbf{O}_SR = \mathbf{N}_W \times \frac{\mathbf{S}}{\mathbf{B}} + \mathbf{N}_R \times \frac{\mathbf{S}}{\mathbf{B}}
\label{eqn:storage}
\end{equation}
where $\mathbf{N}_W$ is the total number of times Revolve writes checkpoints for a single run, $ \mathbf{N}_R$ 
is the number of times checkpoints are read, and $\mathbf{B}$ is the memory bandwidth of the target system.

>>>>

When the memory available on a system is less than $\mathbf{S} \times \mathbf{N}$, Revolve provides
an optimal strategy to solve for the adjoint field by storing a subset of the $\mathbf{N}$ total checkpoints
and recomputing the remaining ones. The overhead introduced by this method can be broken down into
the recomputation overhead $\mathbf{O}_R$ and the storage overhead $\mathbf{O}_S$. The recomputation
overhead is simply the amount of time spent in recomputation, given by:
\begin{equation}
\mathbf{O}_R(N, M) = p(N, M) \cdot \mathbf{C}
\end{equation}
where $p(N, M)$ is the minimum number of recomputed steps from TODO cite revolve, reproduced
here in equation \ref{eqn:recompute}.
\begin{figure*}
\begin{equation}
\mathbf{O}_R(N, M) = \begin{cases}
      N(N-1) /2, & \text{if}\ M=1 \\
      \min\limits_{1<=\widetilde{N}<=N} \{\widetilde{N} + \mathbf{O}_R(\widetilde{N}, M) + \mathbf{O}_R(N-\widetilde{N}, M-1)\}, & \text{if}\ M>1
    \end{cases}
    \label{eqn:recompute}
\end{equation}
\end{figure*}
In equation \ref{eqn:recompute}, M is the number of checkpoints that can be stored in memory. Note that for $M >=N$, $\mathbf{O}_R$
would be zero. For $M < N$, $\mathbf{O}_R$ goes up rather quickly as M is reduced in relation to N.

In a perfect implementation, the storage overhead $\mathbf{O}_S$ might be zero, since the computation could
be done "in-place", but in practice, checkpoints are generally stored in a separate section of memory and they
need to be transferred to a "computational" section of the memory where the compute is performed, and then
the results copied back to the checkpointing memory. This copying is a common feature of checkpointing
implementations, and might pose a non-trivial overhead in scenarios where the computation is heavily bandwidth-bound. 
This storage overhead is given by:
\begin{equation}
\mathbf{O}_SR = \mathbf{N}_W \cdot \frac{\mathbf{S}}{\mathbf{B}} + \mathbf{N}_R \times \frac{\mathbf{S}}{\mathbf{B}}
\label{eqn:storage}
\end{equation}
where $\mathbf{N}_W$ is the total number of times Revolve writes checkpoints for a single run, $ \mathbf{N}_R$ 
is the number of times checkpoints are read, and $\mathbf{B}$ is the memory bandwidth of the target system.
